\TheTitle

### 2015-08-17 linvis.tex
Formatting: Minor changes

\newif\ifdraft
\drafttrue

@@

The second tab is the files tab. This tab provides information on what files
have been edited, how many lines were added, and how many lines were removed in
a given commit. This functionality is similar to the other tools available. Our
tree-based design model allows us to extend this functionality to merges, which
the other tools are unable to show. When a file is edited multiple times from
different commits within a merge, we simply add the added and removed lines to
the values already stored.

@@

We use similar methods to generate the file information and the tree. Both are
generated asynchronously, allowing us to use spinners to help improve the user
experience. We are using AJAX requests to generate the asynchronous requests,
are are having very good results.

@@

\subsection{Performance}
The modules and list tree view still use the old method of gathering the
information for the respective view type. For single commits or very small
merges, getting everything directly from the database and generating the pages
server-side performs better than using the asynchronous requests, there
isn't the overhead of multiple round trips. As the size of the merges grow,
the performance becomes far worse than the asynchronous system and in some
cases will time out. The asynchronous approach adds some overhead, profiled at
roughly 500ms, regardless of the response size. The asynchronous approach has
many benefits over building the response on the server, including spinners, a
public API, and lower response times for larger merges. Further work can be
done to improve the results beyond the response time of 500ms using improved
queries and more efficient methods of building the tree.

\section{Conclusion}
Our tool shows promising results, providing a clearer picture of the relation
between the merges and commits when compared to DAG-based models. Not only are
we provide a clearer visualization, we provide information about the files
edited by all of the commits contained within a merge, and we provide the
information about what modules are edited in a merge.

>>>>

\newif\ifdraft
% \drafttrue

@@

The second tab is the files tab. This tab provides information on what files
have been edited, how many lines were added, and how many lines were removed in
a given commit. This functionality is similar to the other tools available. Our
tree-based design model allows us to extend this functionality to merges, which
the other tools are unable to show. When a file is edited multiple times from
different commits within a merge, we simply add the added and removed lines to
the values already stored.\newpage

@@

We use similar methods to generate the file information and the tree. Both are
generated asynchronously, allowing us to use spinners to help improve the user
experience. We are using AJAX requests to generate the asynchronous requests,
are are having very good results.\newpage

@@

\subsection{Performance}
The modules and list tree view still use the old method of gathering the
information for the respective view type. For single commits or very small
merges, getting everything directly from the database and generating the pages
server-side performs better than using the asynchronous requests, there
isn't the overhead of multiple round trips. As the size of the merges grow,
the performance becomes far worse than the asynchronous system and in some
cases will time out. The asynchronous approach adds some overhead, profiled at
roughly 500ms, regardless of the response size. The asynchronous approach has
many benefits over building the response on the server, including spinners, a
public API, and lower response times for larger merges. Further work can be
done to improve the results beyond the response time of 500ms using improved
queries and more efficient methods of building the tree.\newpage
\section{Conclusion}
Our tool shows promising results, providing a clearer picture of the relation
between the merges and commits when compared to DAG-based models. Not only are
we provide a clearer visualization, we provide information about the files
edited by all of the commits contained within a merge, and we provide the
information about what modules are edited in a merge.
